\section{Problem Files}
  To write a problem using \LaTeX ML, you must first understand the basics 
  of the XML encoding being used.
  
  \subsection{Problem XML Specification}
    Here is a sample problem, for the sake of explanation:
{
  \newcommand\TB{\hspace*{1em}}
    \begin{mdframed}
      \texttt{
<problem>\\
\TB<usedin year=}``\textit{2015}''\texttt{>}Homework 5\texttt{</usedin>\\
\TB<usedin year=}``\textit{2014}''\texttt{>}Midterm 1\texttt{</usedin>\\
\TB<version id=}``\textit{2}''\texttt{>\\
\TB\TB<author>}cjk\texttt{</author>\\
\TB\TB<year>}2016\texttt{</year>\\
\TB\TB<topics>}number\_theory graph\_theory\texttt{</topics>\\
\TB\TB<types>}proof induction\texttt{</types>\\
\TB\TB<param name=}``\textit{modulus}''\texttt{>}3\texttt{</param>\\
\TB\TB<dependency>}tikz\texttt{</dependency>\\
\TB\TB<body>}\\
\TB\TB\TB The modulus is \textbf{\textbackslash modulus}.\\
\TB\TB\texttt{</body>\\
\TB\TB<solution>}\\
\TB\TB\TB Solution to problem goes 
  \textbf{\textbackslash textit}\texttt{\{}\textit{here}\texttt{\}}\\
\TB\TB\texttt{</solution>\\
\TB\TB<rubric>\\
\TB\TB\TB}Problem rubric goes here\texttt{\\
\TB\TB</rubric>\\
\TB</version>\\
\TB<version id=}``\textit{1}''\texttt{>\\
\TB\TB...\\
\TB</version>\\
</problem>
}
    \end{mdframed}
}
    \textbf{A problem XML file must have the extension `.xml' or it will 
    not be incorporated into PDF builds.}
    
    \textbf{A Problem XML file MUST have root tag \texttt{problem}, which 
    is made up of one or more child \texttt{version}s.} Loosely speaking, 
    two `versions' should be part of the same `problem' if having the 
    solution to one would make writing the other's solution trivial. For 
    example: adding a part to, theming, or changing the numbers in a 
    previous year's problem would call for a new version of the problem. 
    If several different problems are combined into one, that is generally 
    a new problem (rather than a version of any of them).
    
    \textbf{Each version MUST have exactly one year} (in a \texttt{<year>} 
    tag), which may be ``Unknown''. This is the year that the version was 
    written.
    
    \textbf{Each version MUST have at least one author, at least one 
    topic, and at least one type.} Each of these tags accepts a whitespace 
    separated list of items; thus,
    \begin{center}
      \texttt{<authors>}cjk nschank\ \ \ kl47\texttt{</authors>}
    \end{center}
    would be parsed as three authors: cjk, nschank, and kl47. Additional 
    instances of a tag will append to the list, so e.g. multiple 
    \texttt{<author>} tags within a version are allowed.
    
    Each of these fields accepts both the singular and plural of their 
    tagname, purely for convenience. Thus...
    \begin{description}\itemsep0pt
      \item[Authors] \texttt{<author>} or \texttt{<authors>}
      \item[Topic] \texttt{<topic>} or \texttt{<topics>}
      \item[Type] \texttt{<type>} or \texttt{<types>}
    \end{description}
    
    Note that, while either tagname is accepted, the beginning and ending 
    tags must match.
    
    See the next section for an explanation of acceptable values for topic 
    and type.
    
    \textbf{Each version MUST have a body, a solution, and a rubric.} 
    Each of these fields may be filled with arbitrary \LaTeX; whatever you 
    would have put between \texttt{\textbackslash begin\{document\}} and 
    \texttt{\textbackslash end\{document\}} goes here. It is expected 
    that, if a solution or rubric is not complete, the four letters ``TODO'' 
    (case insensitive) should appear somewhere within their text. This 
    allows the \LaTeX ML tools to keep track of any problems that need 
    attention. (See the command cheat sheet for an example of how you can use
    this feature.)
    
    As an important note, the characters \&\ and $<$ are special 
    characters within XML. In order for the problem to be parsed, you MUST 
    escape them with the XML sequences \texttt{\&amp;}, \texttt{\&lt;}, 
    and \texttt{\&gt;} respectively. They will be unescaped before being 
    parsed as \LaTeX, so should be treated identically to their 
    corresponding characters (e.g. tables will contain many instances of ``
    \texttt{\&amp;}'').
    
    \textbf{Each version MUST have an \texttt{id} attribute, unique within 
    the problem, set to a positive integer, such that the newest version 
    has the highest ID.}
    
    A version MAY have zero or more \texttt{param} or, equivalently, 
    \texttt{parameter} tags, which MUST have a \textit{name} attribute. This is 
    equivalent to temporarily creating a command \texttt{\textbackslash 
    name} which produces the value given in the tag's field. In the 
    provided example, the command ``\texttt{\textbackslash modulus}'' will 
    evaluate to 3. This field is intended for use within problems that can 
    be easily changed without needing to create a new version. As an 
    example, the name of a person or object within a problem should be 
    refactored into a parameter, so that the problem can be changed more easily.
    
    A version MAY have zero or more \texttt{dependency} (also allowed: 
    \texttt{dep}, \texttt{deps}, \texttt{dependencies}) tags, each of 
    which should be a whitespace-separated list of packages which are 
    required in order to build the problem. \texttt{tikz} is the most 
    commonly included by far. These dependencies will by dynamically 
    imported when building an assignment including this problem.
    
    \texttt{usedin} tags should never be created or edited by hand.
  
  \subsection{Topics}
    A \textbf{topic} is a unit of the class which a question is attempting 
    to focus on. A problem-version may have multiple topics (we encourage 
    it!), and the topics should be kept specific but not overly so. Any 
    unrecognized topic within a topic list is considered a fatal error.
    
    Allowed topics are:
    \begin{itemize}\itemsep0pt
      \item basic\footnote{The `basic' topic should be included on 
      anything that could go on the first homework, before we have really 
      introduced any definitions. As an example, \textit{Prove that $\sqrt 
      2$ is irrational} would be in the basic topic.}
      \item big\_o
      \item bijections
      \item circuits
      \item counting
      \item equivalence\_relations
      \item graph\_theory
      \item logic
      \item mod
      \item number\_theory
      \item pigeonhole
      \item probability
      \item relations
      \item set\_theory
      \item todo\footnote{If the topics field of a version should be 
      looked at later (e.g. you are unsure about one and want to return to 
      it), \textit{always} include todo as a topic.}
    \end{itemize}
    
    If ever confused about what topic(s) a problem covers, consider that 
    the topics field is meant to be organizational. Keep two questions in mind:
    
    \begin{enumerate}[1.]\itemsep0pt
      \item If Carly were making the final exam, and wanted to include a 
      question on this topic, would she want to see this problem? If so, 
      include the topic!
      \item Does the question mention or incorporate a topic, even if the 
      question doesn't seem to be ``about'' that topic? For instance, does 
      this graph theory question define a relation? Is this probability 
      question asking about circuits? Always include \textit{both} topics 
      -- we like to include questions that bring together multiple units, 
      so that students can find connections and recall old definitions.
    \end{enumerate}
  
  \subsection{Types}
    A \textbf{type} is a characteristic of the question itself, and is 
    equivalent to a `tag' in many other contexts. (The name `type' is used 
    to differentiate from an XML tag.) Like topics, questions can (and 
    usually do) have multiple types. Any unknown type is a fatal error.
    
    The acceptable types (and their meanings):
    \begin{description}
      \item[computation] Any part of the question requires numerical 
      computation \textit{with little justification}, or asks for an 
      explicit instance of something.
      
        \textit{Examples}: Encrypt this using RSA; determine the size of 
        this set; provide a coloring of this graph; use Chinese Remainder 
        Theorem; show these logical statements are equivalent using set 
        algebra.
      
        \textit{Non-example}: Convert these logical expressions to English 
        (see \textbf{notation}); counting questions (these usually require 
        justification)
      \item[core] This question is an extremely common question that is 
      definitely simple to Google, but also very important to the class. 
      Some subset of these questions are proven in class every year.
      
        \textit{Examples}: Prove the infinitude of primes; prove that 
        $\mod$ is an equivalence relation; prove that there are an equal 
        number of odd- and even-cardinality subsets of any set.
      \item[contradiction] Any part of the question explicitly asks for a 
      proof by contradiction, or it is the only feasible way to solve the 
      problem.
      \item[contrapositive] Any part of the question is a proof by 
      contrapositive.
      \item[direct] Any part of the question explicitly asks for a direct 
      proof, or it is the only feasible way to solve the problem.
      \item[element\_method] Any part of the question asks for a proof 
      that two sets are equal. (It does not need to say `element method' 
      explicitly.)
      \item[induction] Any part of the question is a proof by induction.
      \item[large] This question has multiple ($>3$) \textit{small} parts 
      \textit{that build upon each other}, generally while getting 
      progressively harder. If you think your question is hard or long, 
      but it does not satisfy the previous sentence, you should fix that.
      
      As a general note, the first part of a `large' problem should be 
      very easy (often just a computation question meant to ease the 
      student in). See a later section on writing good problems.
      \item[needs\_work] If you come across a problem that you think needs 
      to be looked at again or rewritten, add the `needs\_work' type so 
      that someone can come look at it. 
      \item[notation] This question is meant to help the student practice 
      notation.
      
        \textit{Example}: Put this into set-builder notation.
      \item[piece] This question is very short, and could probably be 
      incorporated into another problem. This type is a bit subtle: in 
      general, a `piece' is a question that has one or two parts (usually 
      short proofs) that are not all that interesting by themselves. They 
      are called `pieces' because, when trying to come up with interesting 
      problems, we can use several of them as inspiration to build a `
      large' problem with many small parts.
      
        \textit{Example}: ``Given a set of 52 distinct integers, show that 
        there must be 2 whose sum or difference is divisible by 100.'' 
        Easy and not very interesting, but could be used very well as a 
        lead-in to a question about a more general property of 
        divisibility and pigeonhole.
      \item[proof] Any part of the question asks for a non-trivial proof. 
      \item[repetitive] A question which asks you to do the same thing to 
      several different examples.
      
        \textit{Example}: For each of the following relations, state 
        whether they are injective, surjective, or both; turn the 
        following logical expressions into circuits.
      \item[todo] If the types field of a version should be looked at 
      later (e.g. you are unsure about one and want to return to it), 
      \textit{always} include todo as a type.
    \end{description}
    
  \subsection{Usage}
    The next two sections cover how to effectively edit and render problem 
    files.